\papertitle

### 2012-10-13 manuscript.tex
Fixup intro

%TODO Ryan's paragraph
\cite{Jung1998Range}\cite{Hyams1999Cooperative}\cite{Mehta2006Adaptive}
\cite{Rudol2008Micro}\cite{Luo2011Air}

%TODO Add in final paragraph to lead-in to our work

@@

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) implements a sampling
approach to motion tracking via na\"{i}ve background subtraction, e.g. frame 
differencing[CITATION]. On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.

@@

Na\"{i}ve background subtraction is brittle to changes in a scene over 
time [CITATION]. However, we find it very efficient, and sufficiently 
reliable for the short time spans--less than five seconds--necessary for 
H$^2$Bird to successfully negotiate narrow openings. Calculating $f_0$ 
using a more sophisticated background extraction would retrain the 
underlying motion tracking features of the filter, while providing the 
algorithm with a more robust way of differentiating subject motion from the 
background.

>>>>

The literature on cooperative control of MAVs is similarly limited to larger
vehicles and purely analytical explorations. Nebot, Hyams, and Jung all 
demonstrated cooperative visual servoing for heterogeneous UGVs~\cite{Nebot2003Agents}\cite{Hyams1999Cooperative}\cite{Jung1998Range}. 
Luo and Mehta analyze  UAV-UGV cooperation from a modeling perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. 
Rudol demonstrated a cooperative visual servoing system similar with 
UGVs and MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of 
magnitude larger than the millirobotic systems we target, and so were able 
to take advantage of high-performance processors and specialized cameras.

The small size of millirobotic air and ground vehicles necessitates 
specialization, but it also pays dividends agility. A group of specialized 
heterogeneous millirobots can navigate more challenging terrains and 
interact with their environments in ways that larger, monolithic vehicles 
cannot. Despite this advantage, in order to collectively equal the sensing and 
computational capabilities of larger robots, they will also have to interact 
so that multiple robots can benefit from the specialized capabilities of 
cooperating vehicles. Millirobotic systems will benefit from cooperation 
even more than their larger counterparts.

@@

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) implements a sampling
approach to motion tracking via na\"{i}ve background subtraction, e.g. frame 
differencing~\cite{Ahad2011Computer}. On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.

@@

Na\"{i}ve background subtraction is brittle to changes in a scene over 
time~\cite{Ahad2011Computer}. However, we find it very efficient, and sufficiently 
reliable for the short time spans--less than five seconds--necessary for 
H$^2$Bird to successfully negotiate narrow openings. Calculating $f_0$ 
using a more sophisticated background extraction would retrain the 
underlying motion tracking features of the filter, while providing the 
algorithm with a more robust way of differentiating subject motion from the 
background.
